%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[10.5pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true
    urlcolor = cyan
}
% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{David Jinher}{Zhu}
\position{Chemical and Process Engineering PhD Candidate}
\address{11A Viscount Road, Morley, WA, 6062}

\mobile{(+61) 414 216 908}
\email{david.zhu@research.uwa.edu.au}
%\homepage{www.posquit0.com}
\github{davidzhuuwa}
\linkedin{davidzhuu}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world. Now!"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Recruitment Team at Santos Ltd}
  {Level 7 \\ 100 St Georges Terrace \\ Perth \\ Western Australia, 6000}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Re: Santos 2022/2023 Summer Vacation Program}
% How the letter is opened
\letteropening{Dear Recruitment at Santos,}
% How the letter is closed
\letterclosing{Yours Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {David J. Zhu~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
With my strong background in research and flow assurance stemming from my PhD Candidature and my First Class Honours degree in Chemical
Engineering, I am confident that I will be a great fit with the team at Santos in any capacity and location.

%\lettersection{About Me}
My robust research background stems from my PhD and Honours at UWA and my maintenance research internship at Downer Group. My PhD has been focused on developing a more physically robust model for hydrate phase equilibria to improve the prediction accuracy. This work is highly relevant to midstream oil and gas operations in reducing the associated mono-ethylene glycol (MEG) requirement for total inhibition. I chose to pursue a PhD in this field because my passion for chemical engineering stems from my interest in process optimisation. The fulfilment of this undertaking further reinforced this
passion. I wish to expand and apply this knowledge to fields within and
outside this area with Santos, where I can significantly contribute to
engineering projects and work towards Santos's goal of net-zero by 2040. I am in
the penultimate year of PhD and expect to submit my thesis in Q2/Q3 2023. During
my time at university, my exemplary academic record is complimented by a repertoire of teamwork, problem-solving,
communication and leadership skills; I believe these traits and capabilities
make me a valuable addition to Santos.

%\lettersection{Why X?}
I believe my experience will enable me to fit in well with Santos' key
values. My internship at Downer Group in 2016
was the launchpad of my research journey, allowing me to begin
developing my communication skills and extending my knowledge of key
maintenance concepts and technologies within the engineering field. 
Throughout my PhD, I have developed my written and verbal
communication skills extensively through presenting my research to both
technical and non-technical audiences in both poster and oral presentations at
various conferences and symposia. Most recently, I presented at one of UWA's Tieback Symposia
on the new hydrate phase boundary tool I developed in
\href{https://youtu.be/Y--bsK84t_c}{December 2021}, the culmination of my PhD to date then, which was received well by industry members present. The research, analytical and problem-solving skills I have developed during my research career have fostered a creative and critical mindset that encourages innovative thinking. 
%My research
%involved developing a holistic overview of the state of the wireless maintenance
%technologies available, evaluating products regarding cost, availability, size,
%communication technology and much more. I presented these findings to a small group
%of senior management in a short 20-minute presentation, and a 30-page report, and
%was commended highly for my ability to summarise and convey highly technical
%information in a manner that was digestible to an audience with varying
%technical backgrounds. 

%\lettersection{Why Me?}
I value a working and social environment that is safe and conducive for
excellence in the future. From an operational perspective, I have experience of
over 300 hours working in labs with hazardous chemicals and equipment at the
Australian Resources Research Centre (ARRC) for my honours thesis. I also
conduct safety inspections for my research group at both ARRC and UWA
laboratories every second month. Additionally, I have also undertaken numerous lab
demonstrations for third-year engineering students, where I was solely responsible for their supervision and informed them of the necessary safety requirements before entry and during the laboratory session. These experiences have instilled the importance of identifying hazards and implementing thorough risk management plans, leading me to be constantly aware of my peers and surroundings and ensuring I wear the appropriate PPE. From a social perspective, my experience as a
Postgraduate Unimentor at UWA and an Academic Tutor have exposed me to various students with different learning styles and backgrounds. These experiences have fostered vital skills such as active listening, initiative and cultural awareness, which will serve me well when adjusting to working in a new team in an unfamiliar environment.

Thank you for taking the time to consider my application and review my resume. I look forward to any opportunity to discuss the position and what I can do for Santos. I believe my vision and values align with Santos, and I'd be an excellent fit for the company. My contact details are listed if you require any other information.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
