%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Doctor of Philosophy} % Degree
    {The University of Western Australia} % Institution
    {Crawley, Western Australia} % Location
    {Jan. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        %\item {Courses completed: Reaction Engineering (99\%), Control Engineering (94\%), Treating and LNG Production (94\%), Transport Phenomena (91\%), Flow Assurance and Gathering (94\%); Process Synthesis and Design (96\%); Unit Operations and Processes (87\%)}
        \item {Supervisors: Prof. Zachary M. Aman, Prof. Eric F. May, Dr. Bruce
            W.E. Norris}
        \item{Focus on thermophysical modelling in context of gas hydrate phase
            equilibria}
        \item{One of four core developers for ThermoFAST, a thermodynamic
                property calculator for natural gas, LNG, ammonia and hydrogen
                with the ability to perform vapour-liquid-solid equilibrium
            calculations}
        \item{Developed and implemented novel description of hydrate phase
                equilibrium model in ThermoFAST 2, with draft paper
            in-publication}
        \item{Implemented Cubic plus Association Equation of State in ThermoFAST
            2}
      \end{cvitems}
    }
    
  \cventry
    {Master of Professional Engineering: Chemical Engineering} % Degree
    {The University of Western Australia} % Institution
    {Crawley, Western Australia} % Location
    {Jul. 2017 - Dec. 2019}
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 7.000; WAM: 92.6}
        %\item {Courses completed: Reaction Engineering (99\%), Control Engineering (94\%), Treating and LNG Production (94\%), Transport Phenomena (91\%), Flow Assurance and Gathering (94\%); Process Synthesis and Design (96\%); Unit Operations and Processes (87\%)}
        \item {Final year design project on an ammonia synthesis plant with a natural gas feedstock located in Onslow, Western Australia}
      \end{cvitems}
    }

  \cventry
    {Bachelor of Philosophy (Hons)} % Degree
    {The University of Western Australia} % Institution
    {Crawley, Western Australia} % Location
    {Feb. 2014 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {First Class Honours in Engineering Science (Chemical Engineering); Second Major in Mandarin Chinese (Beginner)}
        %\item {GPA: 6.933; WAM: 87.4}
        \item {Thesis: The effect of Mono-ethylene Glycol on Hydrocarbon Cloud Points via Differential Scanning Calorimetry, with Prof. Zachary Aman (83\%)}
        %\item {Second author to unpublished journal article on same topic as thesis}
        %\item {Relevant courses: (Advanced Thermodynamics (90\%), Particles Mechanics and Solids Handling (91\%), Risk, Reliability and Safety (89\%), Project Management (82\%)}% Fluid Mechanics (92\%), Chemical Thermodynamics and Kinetics (98\%), Heat and Mass Transfer (94\%), Mass and Energy Balances (95\%)}
      \end{cvitems}
    }
    
\cventry
    {Short-term Exchange} % Degree
    {Zhejiang University | Beijing Institute of Education} % Institution
    {Hangzhou, China | Beijing, China} % Location
    {Dec. 2014 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Exchange with Zhejiang University / Beijing Institute of
            Education for 6 weeks each, focused on developing written and oral Mandarin Chinese communication skills}
      \end{cvitems}
    }
    

  

%---------------------------------------------------------
\end{cventries}
