%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%------------------------------------------------------------------------    
  %\cventry
  %  {The University of Western Australia}
  %  {Academic Tutor}
  %  {Crawley, Western Australia}
  %  {Feb. 2019 - Present}
  %  {
  %    \begin{cvitems} % Description(s) of tasks/responsibilities
  %      \item {ENSC3006: Chemical
  %         Engineering Thermodynamics (2020-present); ENSC3019: Unit Operations
  %      and Processes (2020-present); CHPR5521: Flow Assurance and Gathering
  %      (2019); CHPR5522: Treating and LNG Production (2019); and GENG4402: Control
  %      Engineering (2019);}

  %     \item {Designed new laboratory demonstrations and accompanying
  %             assignments for ENSC3006 (3 labs) and ENSC3019 (4 labs) in 2020,
  %         ensuring flexibility for hybrid working environments}
  %      \item {Co-supervised and provided technical assistance related to
  %          engineering software (OLGA, AspenHYSYS, MultiFlash) to classes of
  %      40-50 postgraduate students; and}
  %      \item {Enabled students to develop understanding of how the theoretical
  %          concepts introduced in lectures are linked to implementation of the
  %      technical solutions in industrial contexts.}
  %      \item {Control engineering: delivers lessons in two-hours sessions to
  %          classes of 20-30 postgraduate students reinforcing fundamental
  %      concepts introduced in lectures; and}
  %      \item {Developed lesson material supplementing lecturer-supplied content
  %          to enhance students' understanding and ability to retain
  %      information.}
  %    \end{cvitems}
  %  }
  \cventry 
    {The University of Western Australia}
    {Academic Tutor / Facilitator}
    {Crawley, Western Australia}
    {Feb. 2019 - Present}
    {
      \begin{cvitems}
          \item{Designed new laboratory demonstrations and accompanying
                  assignments for ENSC3006 (3 labs) and ENSC3019 (4 labs) in
                  (2020 - Present), ensuring flexibility for hybrid-learning mode.}
          \item {Led weekly open hybrid-consultations for students, assisting them
                  with laboratory-related conceptual queries and/or technical assistance
              with engineering software (MultiFlash, AspenHYSYS); and}
          \item{Enabled students to develop an understanding of how the theoretical
                  concepts introduced in lectures and labs are linked to the implementation
              of technical solutions in industrial contexts.}
           \item {2019: Tutor for GENG4402: Control Engineering,
                   CHPR5521: Flow Assurance and Gathering, and CHPR5522:
               Treating and LNG Production.}
      \end{cvitems}
    }

  \cventry
    {The University of Western Australia}
    {Research Assistant}
    {Crawley, Western Australia}
    {Dec. 2018 - Jan. 2020}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-time summer vacation student transitioned into casual work
            Chevron-Woodside established Centre for Long Subsea Tiebacks}
        \item {Created a database consolidating over 8,000 selected experimental
            hydrate phase equilibrium data points from published literature;}
        \item {Analysed trends in error margins from the experimental data
            against software predictions using the created database to highlight
        areas of model inaccuracy and data sparsity;}
        \item{Active participant in weekly reading group meetings, where two
            papers in the field of "Hydrates Interfacial Science" are presented
        weekly; and}
        \item{Presented four critical review presentations in aforementioned
            reading group meetings, which were received well by senior
        academics.}
      \end{cvitems}
    }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \cventry
    {UWA Young Engineers} % Job title
    {Project Team Member} % Organization
    {Perth, Western Australia} % Location
    {Jun 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{UWA Young Engineers is the student chapter of Engineers Australia
            and our mission is to aid in the professional development of all our
        club members through the organisation of various events;}
        \item {Facilitated club's transition from Google services to Microsoft
            365 (email and cloud storage) in 2021;}
        %\item {Prepared >50 name-tags and >200 wristbands for UWAYE's Industry Analysis Night;}
        \item {Involved as an usher for UWAYE's Industry Analysis Night,
            directing >150 people to and from auditorium at scheduled timing;}
        \item {Created marketing posts for Facebook and printing and
                distribution of posters for multiple hackathon events (2018 -
            WorleyParsons, 2022 - Accenture)}
        %\item {Managed venue hire, printing and distribution of 50 posters as part of marketing for a hackathon held in conjunction with WorleyParsons.}
        %\item{Assisted in setup, set-down, supervision and catering delivery on day of hackathon which ran from 9am until 6pm.}
      \end{cvitems}
    }
    
  \cventry
    {The Revival Fellowship} % Job title
    {Visual-Audio Coordinator | Pianist} % Organization
    {Perth, Western Australia} % Location
    {January 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team Coordinator for Visual/Audio requirements in Church
            services, including streaming live Zoom meetings. Also includes organising weekly
        rosters and training new volunteers.}
        \item {Active pianist for church band. Rostered on Sundays and Wednesdays weekly.}   
      \end{cvitems}
    }    
    
%    \cventry
%    {The Revival Fellowship} % Job title
%    {Team Leader Assistant | Pianist} % Organization
%    {Perth, Western Australia} % Location
%    {Apr 2016 - December 2019} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Voluntary Team leader assistant for a church youth group (one of four teams);}
%        \item {Assists in organising and running social activities monthly; activities run weekly and range from social sports and survivor style games to bible study discussion nights.}
%        \item {Organised events including indoor volleyball, squash, tennis, and dodgeball for 30-40 attendees.}
%        \item {Assists team leader in facilitating discussions and delegating tasks for members to complete at events/camps and encouraging member participation in activities;}
% 
%      \end{cvitems}
%    }
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \cventry
    {The University of Western Australia} % Job title
    {Postgraduate UniMentor} % Organization
    {Crawley, Western Australia} % Location
    {Jun. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitating and supporting transition of commencing postgraduate
            students by drawing on experience and knowledge of Perth and UWA;}
        \item {Facilitating weekly correspondence with mentees online or
            in-person to assist in transition during mentees' first semester;}
        \item {Applying active listening and problem solving skills to assist
            with mentee's queries and problems, redirecting mentees to
        appropriate university services and facilities;}
        \item{Lead a walking tour group of ten international students around the Perth CBD;}
        \item{Mentored three commencing international chemical engineering students.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Downer Group} % Job title
    {Maintenance Research Intern} % Organization
    {Perth, Western Australia} % Location
    {Sep. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched and developed a holistic understanding of maintenance
            strategies, namely how predictive maintenance is used in conjunction
        with condition monitoring and other maintenance strategies;}
        \item {Researched examples of common failure modes in equipment, and
            respective common condition monitoring techniques used in context of
        electric motors;}
        \item {Researched wireless technology use, namely sensors, and compiled
            information about  costs, availability, benefits and drawbacks in
        condition monitoring applications; and}
        \item{Submitted a short report (30 pages) and gave a 20 minute
            presentation on key findings and lessons learned to senior
        management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
  %  {Kumon} % Job title
  %  {Teaching Assistant} % Organization
  %  {Perth, Western Australia} % Location
  %  {Dec 2013 - Mar 2014} % Date(s)
  %  {
  %    \begin{cvitems} % Description(s) of tasks/responsibilities
  %      \item {Assisted students with problem solving and information retrieval in a mathematics and English context;}
  %      \item {Enabled students to develop critical thinking skills and strategies required to understand and apply concepts;}
  %      \item {Assisted teachers with room setup/set down, re-organising tables, chairs and handing out of students' worksheets; and}
  %      \item {Assisted teachers with marking and collation of students' work}
  %    \end{cvitems}
  %  }
    
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    

%---------------------------------------------------------
\end{cventries}
